Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-19 aa workingdraft/draft.tex

>>>>

\begin{figure}[H]
\includegraphics[width=5in]{../pics/flume_with_sedtraps.png}
\centering
\caption{Conceptual diagram of the Ecogeomorphology laboratory flume. Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator. Arrows indicate direction of flow. A side view of the open-channel part of the system is included. Some dimensions not to scale. Red circles in the top-down view and black rectangles in the side view of the test section show the locations of the sediment traps.}
\label{fig:floorplan}
\end{figure}
